### 2022-12-23 output/summary_statistics/tables/balance_table.tex
Updates from Overleaf

\begin{table}[H]
\begin{tabular}{llrrrr}
\toprule
 &  & \multicolumn{2}{c}{Control Group} & \multicolumn{2}{c}{Treatment Group} \\
 &  & Mean & N & Mean & N \\
Panel & Variable &  &  &  &  \\
\midrule
\multirow[c]{8}{4cm}{\textit{Panel A: Case Initiation}} & For cause & 0.12 & 3651 & 0.12 & 10708 \\
 & For cause (transfer) & 0.01 & 3651 & 0.01 & 10708 \\
 & Foreclosure & 0.01 & 3651 & 0.03 & 10708 \\
 & Foreclosure (transfer) & 0.00 & 3651 & 0.00 & 10708 \\
 & No cause & 0.12 & 3651 & 0.10 & 10708 \\
 & No cause (transfer) & 0.02 & 3651 & 0.00 & 10708 \\
 & Non-payment of rent & 0.69 & 3651 & 0.72 & 10708 \\
 & Non-payment of rent (transfer) & 0.03 & 3651 & 0.01 & 10708 \\
\cline{1-6}
\multirow[c]{5}{4cm}{\textit{Panel B: Case Resolution}} & Case defaulted & 0.00 & 3651 & 0.70 & 10708 \\
 & Case involuntarily dismissed & 0.99 & 3651 & 0.00 & 10708 \\
 & Case heard & 0.01 & 3651 & 0.21 & 10708 \\
 & Case mediated & 0.00 & 3651 & 0.00 & 10708 \\
 & Case voluntarily dismissed & 0.00 & 3651 & 0.00 & 10708 \\
\cline{1-6}
\multirow[c]{5}{4cm}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.22 & 3651 & 0.07 & 10708 \\
 & Plaintiff has an attorney & 0.78 & 3651 & 0.81 & 10708 \\
 & Defendant is an entity & 0.01 & 3651 & 0.01 & 10708 \\
 & Plaintiff is an entity & 0.62 & 3651 & 0.67 & 10708 \\
 & Money judgment & 63.61 & 3651 & 3688.76 & 10708 \\
\cline{1-6}
\multirow[c]{5}{4cm}{\textit{Panel C: Assessor Records From Post-Filing F.Y.}} & Total property value & 6478531.48 & 1256 & 8995455.63 & 3992 \\
 & Building value & 1605427.57 & 1256 & 2352344.15 & 3992 \\
 & Land value & 61247.49 & 1256 & 100993.11 & 3992 \\
 & Other value & 8138231.73 & 1256 & 11437647.57 & 3992 \\
 & Units & 41.23 & 1256 & 42.09 & 3992 \\
\cline{1-6}
\multirow[c]{9}{4cm}{\textit{Panel E: Zestimates Around Treatment}} & Five years before latest docket date & 252041.76 & 865 & 279947.69 & 2362 \\
 & Four years before latest docket date & 279493.58 & 875 & 302370.92 & 2388 \\
 & Three years before latest docket date & 308864.59 & 885 & 324126.19 & 2423 \\
 & Two years before latest docket date & 331594.86 & 888 & 348565.94 & 2427 \\
 & One year before latest docket date & 343934.24 & 906 & 372571.00 & 2447 \\
 & Latest docket date & 387984.48 & 920 & 422781.76 & 2471 \\
 & One year after latest docket date & 428426.83 & 899 & 467437.35 & 2402 \\
 & Two years after latest docket date & 451677.43 & 483 & 507407.77 & 1656 \\
 & Three years after latest docket date & 514122.00 & 250 & 502458.89 & 924 \\
\cline{1-6}
\bottomrule
\end{tabular}
\end{table}

>>>>

\begin{table}[H]
\begin{tabular}{llrrrrrr}
\toprule
 &  & \multicolumn{3}{r}{Control Group} & \multicolumn{3}{r}{Treatment Group} \\
 &  & Mean & S.D. & N & Mean & S.D. & N \\
Panel & Variable &  &  &  &  &  &  \\
\midrule
\multirow[c]{8}{3cm}{\textit{Panel A: Case Initiation}} & For cause & 0.12 & 0.33 & 3651 & 0.12 & 0.32 & 10708 \\
 & For cause (transfer) & 0.01 & 0.10 & 3651 & 0.01 & 0.08 & 10708 \\
 & Foreclosure & 0.01 & 0.12 & 3651 & 0.03 & 0.18 & 10708 \\
 & Foreclosure (transfer) & 0.00 & 0.03 & 3651 & 0.00 & 0.04 & 10708 \\
 & No cause & 0.12 & 0.32 & 3651 & 0.10 & 0.30 & 10708 \\
 & No cause (transfer) & 0.02 & 0.12 & 3651 & 0.00 & 0.07 & 10708 \\
 & Non-payment of rent & 0.69 & 0.46 & 3651 & 0.72 & 0.45 & 10708 \\
 & Non-payment of rent (transfer) & 0.03 & 0.18 & 3651 & 0.01 & 0.11 & 10708 \\
\cline{1-8}
\multirow[c]{5}{3cm}{\textit{Panel B: Case Resolution}} & Case defaulted & 0.00 & 0.00 & 3651 & 0.70 & 0.46 & 10708 \\
 & Case involuntarily dismissed & 0.99 & 0.09 & 3651 & 0.00 & 0.00 & 10708 \\
 & Case heard & 0.01 & 0.09 & 3651 & 0.21 & 0.40 & 10708 \\
 & Case mediated & 0.00 & 0.00 & 3651 & 0.00 & 0.00 & 10708 \\
 & Case voluntarily dismissed & 0.00 & 0.00 & 3651 & 0.00 & 0.00 & 10708 \\
\cline{1-8}
\multirow[c]{5}{3cm}{\textit{Panel C: Defendant and Plaintiff Characteristics}} & Defendant has an attorney & 0.22 & 0.42 & 3651 & 0.07 & 0.26 & 10708 \\
 & Plaintiff has an attorney & 0.78 & 0.41 & 3651 & 0.81 & 0.39 & 10708 \\
 & Defendant is an entity & 0.01 & 0.10 & 3651 & 0.01 & 0.09 & 10708 \\
 & Plaintiff is an entity & 0.62 & 0.49 & 3651 & 0.67 & 0.47 & 10708 \\
 & Money judgment & 63.61 & 1217.82 & 3651 & 3688.76 & 7607.02 & 10708 \\
\cline{1-8}
\multirow[c]{5}{3cm}{\textit{Panel C: Assessor Records From Post-Filing F.Y.}} & Total property value & 6478531.48 & 16950095.01 & 1256 & 8995455.63 & 20109262.79 & 3992 \\
 & Building value & 1605427.57 & 4134089.33 & 1256 & 2352344.15 & 6424083.30 & 3992 \\
 & Land value & 61247.49 & 398867.96 & 1256 & 100993.11 & 421815.08 & 3992 \\
 & Other value & 8138231.73 & 20310157.76 & 1256 & 11437647.57 & 25728253.86 & 3992 \\
 & Units & 41.23 & 100.49 & 1256 & 42.09 & 135.69 & 3992 \\
\cline{1-8}
\multirow[c]{9}{3cm}{\textit{Panel E: Zestimates Around Treatment}} & Five years before latest docket date & 252041.76 & 194239.55 & 865 & 279947.69 & 259889.60 & 2362 \\
 & Four years before latest docket date & 279493.58 & 317170.86 & 875 & 302370.92 & 305380.02 & 2388 \\
 & Three years before latest docket date & 308864.59 & 503061.61 & 885 & 324126.19 & 384074.19 & 2423 \\
 & Two years before latest docket date & 331594.86 & 537209.62 & 888 & 348565.94 & 395933.37 & 2427 \\
 & One year before latest docket date & 343934.24 & 324782.38 & 906 & 372571.00 & 316190.70 & 2447 \\
 & Latest docket date & 387984.48 & 362874.22 & 920 & 422781.76 & 426973.62 & 2471 \\
 & One year after latest docket date & 428426.83 & 363569.88 & 899 & 467437.35 & 682448.07 & 2402 \\
 & Two years after latest docket date & 451677.43 & 511837.97 & 483 & 507407.77 & 488063.38 & 1656 \\
 & Three years after latest docket date & 514122.00 & 863333.21 & 250 & 502458.89 & 430807.14 & 924 \\
\cline{1-8}
\bottomrule
\end{tabular}
\end{table}
